Combining formal and distributional models of predicate semantics

### 2016-03-11 papers/acl2016/paper.tex
Minor fixes to paper
Former-commit-id: b8fe45cdc4ed7ae27948c75d0d09d04474e0c829

Our predicate models do not have this limitation.  The distributional component
will still give an unseen entity pair a score of 0, as it is identical to K\&M's
model, but the formal component of our simples simply computes an observed
feature vector from Freebase for the entity pair.  As long as both entities
appear in Freebase, our model can compute a feature vector and give a non-zero
score.

While this improvement allows us to handle queries over rare entities much
better than a distributional-only model, it also complicates inference, as we
cannot just score entity pairs seen at training time.  Optimizing every query's
score over all of the millions of entities in Freebase is not computationally
feasible.  To make inference tractable, for a given query we restrict
candidates to all entities seen with the query entities during training (as
done by K\&M), as well as all entities directly connected to the query entities
in Freebase, or connected by a mediator node\footnote{Mediators in Freebase are
used to capture relations with more than two arguments, such as employment
tenure, which has an employer, and employee, a start date, and an end date.}.

>>>>

Our predicate models do not have this limitation.  The distributional component
will still give an unseen entity pair a score of 0, as it is identical to K\&M's
model, but the formal component of our models simply computes an observed
feature vector from Freebase for the entity pair.  As long as both entities
appear in Freebase, our model can compute a feature vector and give a non-zero
score.

While this improvement allows us to handle queries over rare entities much
better than a distributional-only model, it also complicates inference, as we
cannot just score entity pairs seen at training time.  Optimizing every query's
score over all of the millions of entities in Freebase is not computationally
feasible.  To make inference tractable, for a given query we restrict
candidates to all entities seen with the query entities during training (as
done by K\&M), as well as all entities directly connected to the query entities
in Freebase, or connected by a mediator node.\footnote{Mediators in Freebase are
used to capture relations with more than two arguments, such as employment
tenure, which has an employer, and employee, a start date, and an end date.}
